The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Reorganization of fpt section of paper

We now describe the options available for the function {\tt nu}, and we focus primarily on the case where the second input is an ideal $I$, since the options work analogously when the second input is instead a polynomial $f$.

@@

If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the three forementioned cases, then the function {\tt fpt} next checks whether the polynomial $f$ is a product of factors that are in simple normal crossing, in which case its $F$-pure threshold is easily computed.

@@

>>>>

\subsection*{Options for the {\tt nu} function}

We now describe the options available for the function {\tt nu}.  We focus primarily on the case where the second input is an ideal $I$, since the options work analogously when the second input is instead a polynomial $f$.

@@

If {\tt UseSpecialAlgorithms} is set to {\tt true} and $f$ does not fall into any of the three forementioned cases, then the function {\tt fpt} next calls {\tt isSimpleNormalCrossing(f)} to check whether the polynomial $f$ is a product of factors that are in simple normal crossing.  If this command returns {\tt true}, the $F$-pure threshold can easily be computed, and {\tt fpt} returns this value.  For more detail on the function {\tt isSimpleNormalCrossing} and on computing the $F$-pure threshold of a polynomial with simple normal crossings, please see the end of this section.

@@

\subsection*{The function {\tt isSimpleNormalCrossings}}
